% @Author: oesteban
% @Date:   2014-03-26 15:43:22
% @Last Modified by:   oesteban
% @Last Modified time: 2014-03-26 16:33:23
\begin{tabularx}{\linewidth}{>{\cellcolor{white}}l|>{\cellcolor{white}}l|>{\cellcolor{white}}l|L}
\multicolumn{1}{c}{Database}& \multicolumn{1}{c}{Cohort} & \multicolumn{1}{c}{Seq.} & \multicolumn{1}{c}{MR Parameters} \\
\hline
%
%
 & & T1w & Spoiled FLASH sequence, TR/TE=22/9.2ms, FA (flip angle)=30\degree, $181\times217\times181$ matrix size, 1mm isotropic voxel size. \\
 & & T2w & Dual echo spin echo (DSE), late echo sequence, TR=3300ms, TEs=35,120ms, FA=90$\degree$, $181\times217\times181$ matrix size, 1mm isotropic voxel size. \\
\multirow{-3}{*}{Brainweb$^{1}$} & \multirow{-3}{*}{1 dataset}  & PDw & Dual echo spin echo (DSE), early echo sequence, TR=3300ms, TEs=35,120ms, FA=90$\degree$, $181\times217\times181$ matrix size, 1mm isotropic voxel size. \\
\hline
%
%
 & & T1w & MPRAGE TR/TE/TI=6.7/3.1/842ms, FA=8\degree , $170\times256\times256$ matrix size, $1.0\times1.0\times1.2\,mm^3$ voxel size. \\
 & & T2w & Multi-shot turbo spin echo (TSE), TR/TE=2500/287ms, TSE/SENSE factors=100/2, fat suppression with SPIR, $180\times256\times256$ matrix size, $1.0\times0.9375\times0.9375\,mm^3$ voxel size. \\
 \multirow{-3}{*}{Kirby 21$^{2}$} & \multirow{-3}{*}{\parbox{3.4cm}{21 healthy volunteers \\ (11M/10F, 22-61yr.) }}
 & MT  & Spoiled 3D gradient echo, TR/TE=64/15ms, FA=9\degree, $256\times256\times95$ matrix size, $1.5\times1.5\times1.5\,mm^3$ voxel size.
 \\
\hline
%
%
& & & Philips Medical Systems Intera 3T, MPRAGE TR/TE = 9.6/4.6 ms, FA=8\degree. \\
& & & Philips Medical Systems Gyroscan Intera 1.5T, MPRAGE TR/TE = 9.81/4.6 ms, FA=8\degree. \\
& & \multirow{-3}{*}{T1w} & GE 1.5T System, information undisclosed by the time of accessing. \\
%
& & & Philips Medical Systems Intera 3T, TR/TE = 5725/100.0ms, FA=90\degree.\\
& & & Philips Medical Systems Gyroscan Intera 1.5T, 5725/100.0ms, FA=90\degree. \\
& & \multirow{-3}{*}{T2w} & GE 1.5T System, information undisclosed by the time of accessing. \\
%
& & & Philips Medical Systems Intera 3T, TR/TE = 5725/8.0ms, FA=90\degree. \\
& & & Philips Medical Systems Gyroscan Intera 1.5T, TR/TE = 8178/8.0ms, FA=90\degree. \\
& & \multirow{-3}{*}{PDw} & Philips Medical Systems Gyroscan Intera 1.5T, 5725/100.0ms, FA=90\degree. \\
\multirow{-9}{*}{IXI$^{3}$}
& \multirow{-9}{*}{465 healthy subjects.}
 & & GE 1.5T System, information undisclosed by the time of accessing. \\
\end{tabularx}